---
title: "Extra: Parameterized Reports"
format: qmdrslides-revealjs
---


## Parameterized Reports

#### Use Case

You have a document (pdf, html file, presentation) that you will need to produce many times with only tiny changes.

#### Approach

1. Recode those changes as parameters.
2. Pass parameters during the render process using a script
   - Shell script
   - Python script
   - R script

## Params syntax

Place parameters in YAML under the `params` key.

```yaml
---
params:
  alpha: 0.1
  ratio: 0.1
---
```

You can now access the values inside the `params` R list.

```{r}
#| eval: false
params$alpha
```

```{r}
#| echo: false
0.1
```


## Our Turn

:::{.task}
1. Open `parameterized-reports/grade-report.qmd`.
2. Filter the data set to only use the data of `"Rohan Prakesh"`.
3. Make that a variable accessible through `params`.
4. Add an inline reference to the student.
5. Run `parameterized-reports/make-grade-reports.r`.
:::

## Your Turn

This one is a real challenge!

:::{.task}
1. Create a second qmd called `annual-grade-report.qmd`.
2. Include a few plots that show the aggregate grade performance across all students.
3. Parameterize the report in terms of `year`.
4. Modify the code from `make-grade-reports.r` to produce two grade reports: one for 2023 and one for 2024.
:::