---
title: "Intro to Extensions"
format: qmdrslides-revealjs
---

## Your Turn {.your-turn style="font-size: .9em"}

Refresh your knowledge of markdown by opening `quarto-puzzle.qmd` and adding five features.

_Render after each change to your document to check your progress!_

1. Add an author to the yaml.
2. Convert "Advanced Quarto" to be a level two header.
3. Add a link to the Quarto website (https://quarto.org/) on the word "Quarto" that appears before the comma in the first sentence.
4. Turn the schedule into a bulleted list with 8 items.
5. At the end of the document, insert the image quarto-logo.png found in this directory and make it 150 pixels wide.

```{r}
countdown::countdown(7)
```


## Document filters

> Add specific functionality to a document by modifying its structure during the render process.

. . .

> The modification is done by a Lua script.


## Filters as a Quarto Extension

:::{style="text-align: center"}
```{=html}
<iframe src="https://quarto.org/docs/extensions/" title = "Quarto Extensions" frameborder="1" height="600" width="1300" style="border: 1px solid black"></iframe>
```
:::

::: aside
Source: <https://quarto.org/docs/extensions/>
:::


## Adding an Extension {.our-turn}

In your document directory run at the terminal:

```bash
quarto add < github name >/< repo name >
```

\

### Example

To get the quarto-puzzle filter on any doc:

```bash
quarto add qmdr/quarto-puzzle
```

then in the document yaml

```yaml
---
filters:
  - quarto-puzzle
---
```

## Shortcodes

> A document filter that will inject particular content into your document at the location of your shortcode.

```markdown
This is a paragraph in my document.

{{ < shortcode_name arg1 arg2 etc >}}

Here is a nother paragraph after the shortcode.
```

## Your Turn {.your-turn}

Choose your own extension! Select one of the following shortcode extensions to add to your documents.

1. *Font Awesome*

   <https://github.com/quarto-ext/fontawesome>

2. *QR Code*

   <https://github.com/jmbuhr/quarto-qrcode>

```{r}
countdown::countdown(4)
```


